A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-25 paper/main.tex
add Aliko (2020) and Eickhoff (2020) to Introduction

\section*{Keywords}
% maximal 8
annnotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest

@@

\section*{Introduction}
Cognitive neuroimaging research is moving towards studying brain behavior
under conditions of real-life-like complexity. Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called ``naturalistic stimuli''.

% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall usually short
of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onset and offset of each
sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
audio-description (i.e. the audio-only variant of the
movie)\citep{ForrestGumpGermanAD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
\todo[inline]{importance/bottleneck of (missing) annotations -> Aliko (2020)}
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of aspects of spoken language ranging from a speaker's
identity, to phonology, grammar, syntacs, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

>>>>

\section*{Keywords}
% maximal 8
annotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest

@@

\section*{Introduction} Cognitive and psychiatric neuroimaging are moving
towards studying brain functions under conditions of real-life-like complexity
\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
\citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not,
lerner2011topographic} are increasingly utilized as so called ``naturalistic
stimuli''.

% data-driven methods
Naturalistic stimuli are usually not designed for research purposes but to
entertain their audience. Hence, their temporal is structure usually unknown due
to an ``annotation bottleneck'' \citep{aliko2020naturalistic}. Data-driven
methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or
independent component analysis (ICA)\citep{bartels2004chronoarchitecture} are
often used to analyze corresponding fMRI data circumventing this bottleneck.
However, data-driven methods alone fall usually short of pinpointing their
results to specific stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to test
hypotheses on specific brain functions under more ecologically valid conditions,
to statistically control confounding stimulus features, and to explain not just
``how'' the brain is responding to a stimulus but also ``why''
\citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

% we:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onset and offset of each
sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
audio-description (i.e. the audio-only variant of the
movie)\citep{ForrestGumpGermanAD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why even bother?
This publication enables researchers to model hemodynamic brain responses that
correlate with a variety of aspects of spoken language ranging from a speaker's
identity, to phonology, grammar, syntax, and semantics.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimuli.
